---
title: "LPA and SC"
output: html_notebook
---

```{r}
suppressPackageStartupMessages({
  library("here")
  library("tidyverse")
  library("MplusAutomation")
  library("gt")
  library("glue")
  library("kableExtra")
  library("misty")
  library("lavaan")
  library("AICcmodavg")
  library("nonnest2")
  library("DiagrammeR")
  library("lavaan")
  library("tidyLPA")
  library("semTools")
  library("brms")
  library("MBESS")
  library("ufs")
  library("robmed")
  library("careless")
  library("mice")
  library("psych")
  library("BayesFactor")
  library("effectsize")
  library("tidybayes")
  library("emmeans")
  library("bayesplot")
  library("patchwork")
  library("bmlm")
})

# install.packages("cmdstanr", repos = c("https://mc-stan.org/r-packages/", getOption("repos")))


options("max.print" = .Machine$integer.max)

# Make random things reproducible
set.seed(1234)

options(mc.cores = 4)

bayesplot_theme_set()
```

```{r}
source(here::here("src", "functions", "funs_add_neoffi60_subscales.R"))
source(here::here("src", "functions", "funs_correct_iesr_scores.R"))
source(here::here("src", "functions", "funs_plot_job_qualification.R"))
source(here::here("src", "functions", "funs_generate_all_items_df.R"))

scale_this <- function(x) as.vector(scale(x))

sum_coding <- function(x, lvls = levels(x)) {
  # codes the first category with -1
  nlvls <- length(lvls)
  stopifnot(nlvls > 1)
  cont <- diag(nlvls)[, -nlvls, drop = FALSE]
  cont[nlvls, ] <- -1
  cont <- cont[c(nlvls, 1:(nlvls - 1)), , drop = FALSE]
  colnames(cont) <- lvls[-1]
  x <- factor(x, levels = lvls)
  contrasts(x) <- cont
  x
}
```


# Get data

```{r}
all_items <- generate_all_items_df()
```

There is a problem with IES-R, in the control group. I shift the control distribution of IES-R towards lower values.

```{r}
temp <- correct_iesr_scores(all_items)
all_items <- temp
```


```{r}
ggplot(all_items, aes(x = iesr_ts, colour = is_rescue_worker)) +
  geom_density()
```

```{r}
all_items |> 
  ggplot(aes(y=iesr_ts, fill=is_rescue_worker)) + 
    geom_boxplot() +
    scale_y_log10()
```



```{r}
all_items$y <- all_items$iesr_ts + 0.001

all_items |> 
  group_by(is_rescue_worker) |> 
  summarize(
    # gm_iesr = geometric.mean(y, na.rm = TRUE),
    avg_iesr = mean(y, na.rm = TRUE)
  )
```

There are some cases in which the RWs of Toscana and Lombardia did not have the proper qualification. They are assigned to the category of RWs.

```{r}
all_items$idx <- 1:nrow(all_items)
all_items$is_rescue_worker <- as.character(all_items$is_rescue_worker)
all_items$is_rescue_worker <- ifelse(
  all_items$idx < 746, "Si", all_items$is_rescue_worker
)
all_items$idx <- NULL
```


```{r}
all_items$commeetee_location <- ifelse(
  all_items$is_rescue_worker == "No", "None", all_items$red_cross_commeetee_location
) |> 
  factor()
```

```{r}
all_items$commeetee_location <- ifelse(
  all_items$is_rescue_worker == "No" & all_items$age < 25, "students", all_items$commeetee_location
)
```

```{r}
all_items$commeetee <- ifelse(
  all_items$is_rescue_worker == "No" & all_items$age >= 25, "community_sample",
  all_items$commeetee_location
)

all_items$commeetee <- 
  ifelse(is.na(all_items$commeetee), "community_sample", all_items$commeetee) |> 
  factor()

sum(is.na(all_items$commeetee))
```

```{r}
# all_items <- all_items %>%
#   mutate(job_qualification = case_when(
#     is_rescue_worker=="Si" & job_qualification == "non_rescue_worker" ~ "team_member",
#     TRUE ~ job_qualification)) 
```


## IES-R as a function of group

iesr_ts | trunc(lb = 0) ~ is_rescue_worker + (1 | commeetee),

```{r}
m0 <- brm(
  bf(iesr_ts ~ is_rescue_worker),
  family = hurdle_gamma(),
  data = all_items,
  backend = "cmdstanr"
  # algorithm = "meanfield"
)
```

```{r}
pp_check(m0)
```


```{r}
summary(m0)
```

```{r}
me <- conditional_effects(
  m0, "is_rescue_worker"
)
plot(me, points = FALSE)
```

```{r}
BFt <- BayesFactor::ttestBF(
  all_items$ies_ts[all_items$is_rescue_worker == "Si"], 
  all_items$ies_ts[all_items$is_rescue_worker == "No"],
  paired = FALSE
)
effectsize(BFt)
```

Supported families are:
'acat', 'asym_laplace', 'bernoulli', 'beta', 'beta_binomial', 'binomial', 'categorical', 'com_poisson', 'cox', 'cratio', 'cumulative', 'custom', 'dirichlet', 'dirichlet2', 'discrete_weibull', 'exgaussian', 'exponential', 'frechet', 'gamma', 'gaussian', 'gen_extreme_value', 'geometric', 'hurdle_cumulative', 'hurdle_gamma', 'hurdle_lognormal', 'hurdle_negbinomial', 'hurdle_poisson', 'info', 'inverse.gaussian', 'logistic_normal', 'lognormal', 'multinomial', 'negbinomial', 'negbinomial2', 'poisson', 'shifted_lognormal', 'skew_normal', 'sratio', 'student', 'von_mises', 'weibull', 'wiener', 'zero_inflated_asym_laplace', 'zero_inflated_beta', 'zero_inflated_beta_binomial', 'zero_inflated_binomial', 'zero_inflated_negbinomial', 'zero_inflated_poisson', 'zero_one_inflated_beta'


The sk, ch, mi sub-scales are coded so that high values indicate high self-compassion levels.
The sj, is, oi sub-scales are coded so that high values indicate low self-compassion levels.

The ts_sc score has been computed by reversing the coding of the items of the sj, is, oi sub-scales (so that they indicate the absence of self-judgment, absence of isolation, absence of over-identification).

```{r}
scs_subscales <- with(all_items, data.frame(sk, ch, mi, sj, is, oi, scs_ts))
cor(scs_subscales) |> round(2)
```


## COPE scale

In the COPE scale only two factors are identified.

```{r}
all_items$pos_reinterpretation <- with(all_items, cope_1 + cope_29 + cope_38 + cope_59)
all_items$mental_disengagement <- with(all_items, cope_2 + cope_16 + cope_31 + cope_43) 
all_items$venting <- with(all_items, cope_3 + cope_17 + cope_28 + cope_46) 
all_items$seeking_instrumental_support <- with(all_items, cope_4 + cope_14 + cope_30 + cope_45) 
all_items$active_coping <- with(all_items, cope_5 + cope_25 + cope_47 + cope_58)  
all_items$denial <- with(all_items, cope_6 + cope_27 + cope_40 + cope_57) 
all_items$religion <- with(all_items, cope_7 + cope_18 + cope_48 + cope_60) 
all_items$humor <- with(all_items, cope_8 + cope_20 + cope_36 + cope_50) 
all_items$behavioral_disengagement <- with(all_items, cope_9 + cope_24 + cope_37 + cope_51) 
all_items$restraint <- with(all_items, cope_10 + cope_22 + cope_41 + cope_49) 
all_items$seeking_emotional_support <- with(all_items, cope_11 + cope_23 + cope_34 + cope_52) 
all_items$substance_use <- with(all_items, cope_12 + cope_26 + cope_35 + cope_53) 
all_items$acceptance <- with(all_items, cope_13 + cope_21 + cope_44 + cope_54) 
all_items$suppr_competing_activities <- with(all_items, cope_15 + cope_33 + cope_42 + cope_55) 
all_items$planning <- with(all_items, cope_19 + cope_32 + cope_39 + cope_56) 
```

Create COPE sub-scales scores using *all* items -- note that SEM analyses suggest 
to drop some of the items.

```{r}
all_items$active_coping <- with(
  all_items, pos_reinterpretation + active_coping +
  suppr_competing_activities + planning + restraint + 
    seeking_instrumental_support + acceptance
)

all_items$avoidance_coping <- with(
  all_items, mental_disengagement + denial + humor +
  behavioral_disengagement + substance_use + religion 
)

all_items$soc_emo_coping <- with(
  all_items, seeking_instrumental_support +
  seeking_emotional_support + venting
)
```


## Self-compassion scale


```{r}
plot(density(all_items$scs_ts))
```


```{r}
fit_1 <- brm(
  bf(
    scs_ts ~ is_rescue_worker,
    sigma ~ is_rescue_worker
    ),
  family = student(),
  backend = "cmdstanr",
  data = all_items
)
```

```{r}
pp_check(fit_1)
```


```{r}
me <- conditional_effects(
  fit_1, "is_rescue_worker"
)
plot(me, points = FALSE)
```

```{r}
summary(fit_1)
```

```{r}
BFt <- BayesFactor::ttestBF(
  all_items$scs_ts[all_items$is_rescue_worker == "Si"], 
  all_items$scs_ts[all_items$is_rescue_worker == "No"],
  paired = FALSE
)
effectsize(BFt)
```

```{r}
rw_df <- all_items |> 
  dplyr::filter(is_rescue_worker == "Si")

rw_df <- rw_df %>%
  mutate(job_qualification = case_when(
    job_qualification == "non_rescue_worker" ~ "team_member",
    TRUE ~ job_qualification))
```


## LPA

```{r}
lpa_scales <- c(
  "is_rescue_worker",
  "neuroticism", "extraversion", "openness", "agreeableness", "conscientiousness",
  "active_coping", "avoidance_coping", "soc_emo_coping",
  "iesr_ts",
  # "avoiding", "intrusivity", "hyperarousal",
  # "sk", "ch", "mi", "sj", "is", "oi",
  # "pos_sc",
  # "neg_sc",
  # "ts_sc",
  "mpss_tot"
  # "ptgi_total_score"
  # "relating_to_others",
  # "new_possibilities",
  # "personal_strength",
  # "appreciation_of_life",
  # "spirituality"
)

lpa_rw_df <- subset(rw_df, select=lpa_scales) 

# lpa_rw_df <- subset(all_items, select=lpa_scales) |> 
#   dplyr::filter(is_rescue_worker == "Si")

lpa_rw_df$is_rescue_worker <- NULL

head(lpa_rw_df)
```

```{r}
lpa_rw_df %>% 
  scale() %>%
  estimate_profiles(1:6,
    variances = c("equal", "varying"),
    covariances = c("zero", "varying")
    #package = "MplusAutomation"
  )
```


```{r}
lpa_rw_df %>% 
  scale() %>%
  estimate_profiles(1:6,
    variances = c("equal", "varying"),
    covariances = c("zero", "varying")
    # package = "MplusAutomation"
  ) %>% 
  compare_solutions(statistics = c("AIC", "BIC"))
```



```{r}
m2 <- lpa_rw_df %>%
  scale() %>%
  estimate_profiles(2,
    variances = "varying",
    covariances = "varying",
    package = "MplusAutomation"
  )
```


```{r}
m2_plot <- lpa_rw_df %>%
  scale() %>%
  estimate_profiles(2,
    variances = "varying",
    covariances = "varying",
    package = "MplusAutomation"
    ) %>%
    plot_profiles(add_line = TRUE, rawdata= FALSE, bw = FALSE)
```

Profile 2: dysfunctional
Profile 1: adaptive


```{r}
get_estimates(m2)
```

```{r}
out <- get_data(m2)
lpa_rw_df$lpa_class <- out$Class
```

```{r}
table(
  lpa_rw_df$lpa_class
)
```


```{r}
table(
  lpa_rw_df$lpa_class, rw_df$job_qualification
)
```


```{r}
lpa_rw_df$class <- factor(lpa_rw_df$lpa_class)
summary(lpa_rw_df$class)
```

```{r}
rw_df$class <- lpa_rw_df$class
rw_df$profile <- lpa_rw_df$class
rw_df$profile <- ifelse(
  rw_df$profile == "2", "maladaptive", "adaptive"
)
rw_df$profile <- factor(rw_df$profile)
# Reorder the levels of the 'profile' factor
rw_df$profile <- factor(rw_df$profile, levels = c("maladaptive", "adaptive"))
```

```{r}
m1 <- brm(
  bf(scs_ts ~ profile),
  family = skew_normal(),
  data = rw_df,
  init = 0.1,
  backend = "cmdstanr",
  adapt_delta = 0.9
)
```

```{r}
pp_check(m1)
```


```{r}
summary(m1)
```

```{r}
me <- conditional_effects(
  m1, "profile"
)
plot(me, points = FALSE)
```

```{r}
BFt <- BayesFactor::ttestBF(
  rw_df$scs_ts[rw_df$class == 1], 
  rw_df$scs_ts[rw_df$class == 2],
  paired = FALSE
)
effectsize(BFt, type = "d")
```

```{r}
m1 %>%
  emmeans( ~ profile) %>%
  gather_emmeans_draws() %>%
  ggplot(aes(x = profile, y = .value)) +
  geom_eye() +
  stat_summary(aes(group = NA), fun.y = mean, geom = "line") +
  # facet_grid(~ wool) +
  # theme_light()
  labs(x = "LPA Class", y = "SCS Score", title = "Rescue Workers") +
  papaja::theme_apa() + 
  annotate("text", x = 1, y = 83, label = "Bayesian Cohen's d = 0.89\n 95% CI [0.73, 1.04]")
```



```{r}
names(all_items)
```

### Self-judgment

```{r}
m2 <- brm(
  bf(sj ~ profile),
  data = rw_df,
  family = student,
  backend = "cmdstanr",
  adapt_delta = 0.99
)
```

```{r}
pp_check(m2)
```

```{r}
loo_m2 <- loo(m2)
plot(loo_m2)
```


```{r}
summary(m2)
```


```{r}
me <- conditional_effects(
  m2, "profile"
)
plot(me, points = FALSE)
```

```{r}
emmeans(m2, specs = pairwise ~ profile)
```

```{r}
BFt <- BayesFactor::ttestBF(
  rw_df$sj[rw_df$profile == "adaptive"], 
  rw_df$sj[rw_df$profile == "maladaptive"],
  paired = FALSE
)
effectsize(BFt)
```


```{r}
p2 <- m2 %>%
  emmeans( ~ profile) %>%
  gather_emmeans_draws() %>%
  ggplot(aes(x = profile, y = .value)) +
  geom_eye() +
  stat_summary(aes(group = NA), fun.y = mean, geom = "line") +
  # facet_grid(~ wool) +
  # theme_light()
  scale_x_discrete(labels=c('Low Resilience', 'High Resilience')) +
  labs(x = "LPA Class", y = "SCS Self-Judgment", title = "A") +
  papaja::theme_apa() + 
  annotate("text", x = 1, y = 14.5, label = "Bayesian Cohen's d = 0.82\n 95% CI [0.67, 0.97]")
p2
```

### Isolation

```{r}
m3 <- brm(
  bf(is ~ profile),
  family = skew_normal(),
  data = rw_df,
  backend = "cmdstanr",
  adapt_delta = 0.95
)
```

```{r}
pp_check(m3)
```

```{r}
loo_m3 <- loo(m3)
plot(loo_m3)
```


```{r}
summary(m3)
```


```{r}
me <- conditional_effects(
  m3, "profile"
)
plot(me, points = FALSE)
```

```{r}
emmeans(m3, specs = pairwise ~ profile)
```

```{r}
BFt <- BayesFactor::ttestBF(
  rw_df$is[rw_df$profile == "adaptive"], 
  rw_df$is[rw_df$profile == "maladaptive"],
  paired = FALSE
)
effectsize(BFt)
```

```{r}
p3 <- m3 %>%
  emmeans( ~ profile) %>%
  gather_emmeans_draws() %>%
  ggplot(aes(x = profile, y = .value)) +
  geom_eye() +
  stat_summary(aes(group = NA), fun.y = mean, geom = "line") +
  scale_x_discrete(labels=c('Low Resilience', 'High Resilience')) +
  labs(x = "LPA Class", y = "SCS Isolation", title = "B") +
  papaja::theme_apa() + 
  annotate("text", x = 1, y = 10.2, label = "Bayesian Cohen's d = 0.94\n 95% CI [0.79, 1.10]")
p3
```

### Over-identification


```{r}
m4 <- brm(
  bf(oi ~ profile),
  family = skew_normal(),
  data = rw_df,
  backend = "cmdstanr",
  adapt_delta = 0.99
)
```

```{r}
pp_check(m4)
```

```{r}
loo_m4 <- loo(m4)
plot(loo_m4)
```


```{r}
summary(m4)
```


```{r}
me <- conditional_effects(
  m4, "profile"
)
plot(me, points = FALSE)
```

```{r}
emmeans(m4, specs = pairwise ~ profile)
```

```{r}
BFt <- BayesFactor::ttestBF(
  rw_df$oi[rw_df$profile == "adaptive"], 
  rw_df$oi[rw_df$profile == "maladaptive"],
  paired = FALSE
)
effectsize(BFt)
```

```{r}
p4 <- m4 %>%
  emmeans( ~ profile) %>%
  gather_emmeans_draws() %>%
  ggplot(aes(x = profile, y = .value)) +
  geom_eye() +
  stat_summary(aes(group = NA), fun.y = mean, geom = "line") +
  scale_x_discrete(labels=c('Low Resilience', 'High Resilience')) +
  labs(x = "LPA Class", y = "SCS Over-Identification", title = "C") +
  papaja::theme_apa() + 
  annotate("text", x = 1, y = 9.4, label = "Bayesian Cohen's d = 0.97\n 95% CI [0.82, 1.12]")
p4
```


### Self-kindness

```{r}
m5 <- brm(
  bf(sk ~ profile),
  family = student(),
  data = rw_df,
  backend = "cmdstanr"
)
```

```{r}
pp_check(m5)
```

```{r}
loo_m5 <- loo(m5)
plot(loo_m5)
```


```{r}
summary(m5)
```


```{r}
me <- conditional_effects(
  m5, "profile"
)
plot(me, points = FALSE)
```

```{r}
emmeans(m5, specs = pairwise ~ profile)
```

```{r}
BFt <- BayesFactor::ttestBF(
  rw_df$sk[rw_df$profile == "adaptive"], 
  rw_df$sk[rw_df$profile == "maladaptive"],
  paired = FALSE
)
effectsize(BFt)
```

```{r}
p5 <- m5 %>%
  emmeans( ~ profile) %>%
  gather_emmeans_draws() %>%
  ggplot(aes(x = profile, y = .value)) +
  geom_eye() +
  stat_summary(aes(group = NA), fun.y = mean, geom = "line") +
  scale_x_discrete(labels=c('Low Resilience', 'High Resilience')) +
  labs(x = "LPA Class", y = "SCS Self-Kindness", title = "D") +
  papaja::theme_apa() + 
  annotate("text", x = 1, y = 14.5, label = "Bayesian Cohen's d = 0.28\n 95% CI [0.14, 0.43]")
p5
```

### Common humanity

```{r}
m6 <- brm(
  bf(ch ~ profile),
  family = student(),
  data = rw_df,
  backend = "cmdstanr"
)
```

```{r}
pp_check(m6)
```

```{r}
loo_m6 <- loo(m6)
plot(loo_m6)
```


```{r}
summary(m6)
```


```{r}
me <- conditional_effects(
  m6, "profile"
)
plot(me, points = FALSE)
```

```{r}
BFt <- BayesFactor::ttestBF(
  rw_df$ch[rw_df$profile == "adaptive"], 
  rw_df$ch[rw_df$profile == "maladaptive"],
  paired = FALSE
)
effectsize(BFt)
```


```{r}
p6 <- m6 %>%
  emmeans( ~ profile) %>%
  gather_emmeans_draws() %>%
  ggplot(aes(x = profile, y = .value)) +
  geom_eye() +
  stat_summary(aes(group = NA), fun.y = mean, geom = "line") +
  scale_x_discrete(labels=c('Low Resilience', 'High Resilience')) +
  labs(x = "LPA Class", y = "SCS Common-Humanity", title = "E") +
  papaja::theme_apa() + 
  annotate("text", x = 1.5, y = 12.2, label = "Bayesian Cohen's d = 0.00\n 95% CI [-0.14, 0.14]")
p6
```

### Mindfulness

```{r}
m7 <- brm(
  bf(mi ~ profile),
  family = student(),
  data = rw_df,
  backend = "cmdstanr"
)
```

```{r}
pp_check(m7)
```

```{r}
loo_m7 <- loo(m7)
plot(loo_m7)
```


```{r}
summary(m7)
```

```{r}
emmeans(m7, specs = pairwise ~ profile)
```

```{r}
BFt <- BayesFactor::ttestBF(
  rw_df$mi[rw_df$profile == "adaptive"], 
  rw_df$mi[rw_df$profile == "maladaptive"],
  paired = FALSE
)
effectsize(BFt)
```

```{r}
me <- conditional_effects(
  m7, "profile"
)
plot(me, points = FALSE)
```


```{r}
p7 <- m7 %>%
  emmeans( ~ profile) %>%
  gather_emmeans_draws() %>%
  ggplot(aes(x = profile, y = .value)) +
  geom_eye() +
  stat_summary(aes(group = NA), fun.y = mean, geom = "line") +
  scale_x_discrete(labels=c('Low Resilience', 'High Resilience')) +
  labs(x = "LPA Class", y = "SCS Mindfulness", title = "F") +
  papaja::theme_apa() + 
  annotate("text", x = 1, y = 13.8, label = "Bayesian Cohen's d = 0.32\n 95% CI [0.17, 0.46]")
p7
```

```{r}
fig_scs <- (p2 | p3 | p4) /
(p5 | p6 | p7)

out <- fig_scs + plot_annotation(
  title = 'SCS Subscales as a Function of LPA Profile'
  # subtitle = 'Rescue Workers group'
  # caption = 'Disclaimer: None of these plots are insightful'
)
ggsave("scs_subscales_lpa.pdf", width = 35, height = 20, units = "cm")
```

```{r}
print(out)
```



## IES-R

```{r}
m10 <- brm(
  bf(ies_ts ~ class),
  family = skew_normal(),
  data = rw_df,
  backend = "cmdstanr",
  adapt_delta = 0.99
)
```

```{r}
pp_check(m10)
```

```{r}
summary(m10)
```

```{r}
p10 <- m10 %>%
  emmeans( ~ class) %>%
  gather_emmeans_draws() %>%
  ggplot(aes(x = class, y = .value)) +
  geom_eye() +
  stat_summary(aes(group = NA), fun.y = mean, geom = "line") +
  # facet_grid(~ wool) +
  # theme_light()
  scale_x_discrete(labels=c('Low Resilience', 'High Resilience')) +
  labs(x = "LPA Class", y = "Impact of Event Scale - Revised (IES-R)") +
  # papaja::theme_apa() + 
  annotate("text", x = 1, y = 17, label = "Bayesian Cohen's d = 1.34\n 95% CI [1.18, 1.50]")
p10
```

```{r}
BFt <- BayesFactor::ttestBF(
  rw_df$ies_ts[rw_df$class == 1], 
  rw_df$ies_ts[rw_df$class == 2],
  paired = FALSE
)
effectsize(BFt)
```

```{r}
emmeans(m10 , specs = pairwise ~ class)
```


```{r}
m11 <- brm(
  bf(ptgi_total_score | trunc(lb = 0) ~ class),
  family = student(),
  data = rw_df,
  backend = "cmdstanr"
)
```

```{r}
pp_check(m11)
```

```{r}
summary(m11)
```

### Job qualification

```{r}
rw_df$job_qualification <- ifelse(
  rw_df$job_qualification == "non_rescue_worker", "team_member", 
  rw_df$job_qualification
) 
```


```{r}
m12 <- brm(
  bf(ies_ts ~ job_qualification),
  family = skew_normal(),
  data = rw_df,
  backend = "cmdstanr",
  adapt_delta = 0.99
)
```

```{r}
pp_check(m12)
```

```{r}
summary(m12)
```

```{r}
me <- conditional_effects(
  m12, "job_qualification"
)
plot(me, points = FALSE)
```

```{r}
emmeans(m12 , specs = pairwise ~ job_qualification)
```

```{r}
m13 <- brm(
  bf(scs_ts ~ job_qualification * class),
  family = gaussian(),
  data = rw_df,
  backend = "cmdstanr",
  adapt_delta = 0.99
)
```

```{r}
pp_check(m13)
```

```{r}
me <- conditional_effects(
  m13, "job_qualification:class"
)
plot(me, points = FALSE)
```

```{r}
summary(m13)
```

```{r}
emmeans(m13 , specs = pairwise ~ job_qualification*class)
```

```{r}
m14 <- brm(
  bf(ptgi_total_score ~ ies_total_score | (1 | comme\)),
  family = gaussian(),
  data = rw_df,
  backend = "cmdstanr",
  adapt_delta = 0.99
)
```

```{r}
summary(m14)
```
```{r}
bayes_R2(m14)
```
```{r}
conditional_effects(m14, "is:class")
```


## SEM

```{r}
mydf <- data.frame(
  scs = scale(rw_df$scs_ts),
  class = ifelse(rw_df$class == 1, 0.0, 1.0),
  ptgi = scale(rw_df$ptgi_total_score),
  psc = scale(rw_df$sk + rw_df$ch + rw_df$mi),
  nsc = scale(rw_df$sj + rw_df$oi + rw_df$is),
  commettee = rw_df$red_cross_commeetee_location,
  id = 1:nrow(rw_df)
)

mydf <- mydf[complete.cases(mydf), ]
```

```{r}
# Impute NAs with the mode.
# mydf$commettee[is.na(mydf$commettee)] <- "Comitato di Groane"
# summary(factor(mydf$commettee))
```


```{r}
f1 <- bf(scs ~ class, family = skew_normal())
f2 <- bf(ptgi ~ scs + class, family = skew_normal())
mod <- brm(
  f1 + f2 + set_rescor(FALSE), 
  data = mydf, 
  cores = 4, 
  refresh = 0,
  init = 0.1,
  backend = "cmdstanr",
  adapt_delta = 0.99
)
```

```{r}
bayestestR::mediation(mod, mediator = "scs", ci = 0.95, method = "SPI")
```

```{r}
pp_check(mod, resp = "ptgi")
```

```{r}
pp_check(mod, resp = "scs")
```

```{r}
summary(mod)
```

```{r}
fit <- mlm(d = mydf, 
           id = "commettee",
           x = "class",
           m = "scs",
           y = "ptgi",
           iter = 2000, 
           cores = 4)
```

```{r}
mlm_path_plot(fit, level = .95, text = T,
              xlab = "Resilience\nProfile",
              mlab = "Self\nCompassion",
              ylab = "PTG", digits = 2)
```

# Causal Mediation Analysis for Stan Model

  Treatment: class
  Mediator : scs
  Response : ptgi

Effect                 | Estimate |          95% SPI
----------------------------------------------------
Direct Effect (ADE)    |   -0.300 | [-0.464, -0.140]
Indirect Effect (ACME) |    0.121 | [ 0.053,  0.187]
Mediator Effect        |    0.154 | [ 0.069,  0.230]
Total Effect           |   -0.178 | [-0.325, -0.027]




```{r}
m16 <- brm(
  bf(ptgi_total_score ~ class),
  family = skew_normal(),
  data = rw_df,
  backend = "cmdstanr",
  adapt_delta = 0.99
)
```

```{r}
pp_check(m16)
```


```{r}
summary(m16)
```

```{r}
bayes_R2(m16)
```

```{r}
m17 <- brm(
  bf(ptgi_total_score ~ is_rescue_worker),
  family = skew_normal(),
  data = all_items,
  backend = "cmdstanr",
  adapt_delta = 0.99
)
```


```{r}
summary(m17)
```

```{r}
rw_df$rate_of_activity_num <- as.integer(rw_df$rate_of_activity_num)
```


```{r}
temp <- rw_df[1:746, ]

temp$activity <- cut(
  temp$rate_of_activity_num,
  breaks = c(-1, 0, 1, 2),    
  labels = c("Low", "Medium", "High"),   
  include.lowest = TRUE,    
  ordered_result = TRUE
)   
```

```{r}
m19 <- brm(
  bf(activity ~ class),
  family=cumulative("logit"),
  data = temp,
  backend = "cmdstanr",
  adapt_delta = 0.99
)
```


```{r}
pp_check(m19)
```


```{r}
summary(m19)
```

```{r}
m20 <- brm(
  bf(class ~ last_training_num * scs_ts),
  family=bernoulli(),
  data = temp,
  backend = "cmdstanr",
  adapt_delta = 0.99
)
```

```{r}
summary(m20)
```

```{r}
conditional_effects(m20, "scs_ts:last_training_num")
```


```{r}
table(rw_df$class, rw_df$last_training_num)
```

